Realistically Interesting Domains for Probabilistic Planners

### 2014-04-07 FinalPaper/paper.tex
adjusted ff-replan

% first the title is needed
\title{Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains}

% a short form should be given in case it is too long for the running head
\titlerunning{FF-Replan vs Probabilistic Planner in Real World Domains}

@@

\section{Planners}
\label{sec:planners}

\subsection{FF-Replan}

At the first international probabilistic planning competition IPPC-04, most entries were Markov Decision Processes. The winner, FF-Replan, however was based on deterministic planning techniques.

FF-Replan is an action selection algorithm for online planning in probabilistic domains. Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem. It determinizes the input domain at the start of the planning into a deterministic different domain. They consider two methods of determinization:
\begin{enumerate}
\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics. The performance strongly depends on the methods for choosing the outcomes.
\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a distinct deterministic action. For each possible outcome FF-Replan generates one seperate action for each effect. For nested probabilities, the all-outcomes procedure is applied recursively. This implies that FF-Replan will cease selecting actions whenever it enters a dead state. However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
\end{enumerate}

After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem. This process is repeated when countering an unexpected state until a goal state is reached. It maintains a partial state-action mapping using a hash-table which is initially empty. Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF. It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table. The first action of the plan is then executed in the environment, returning a new state. This partial policy is this produces in an online fashion. It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.

FF-Replan has some obvious shortcomings as it first determinizes the input domain, removing all probabilistic information from the problem and then synthesizes a plan. If an unexpected state should occur whilst executing, the planner replans in the same determinization. It also does not consider multiple potential effects if an action.

By relying on search, FF-Replan could function with enormous speed and efficiency. However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short. Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors are hoping to achieve this.

@@

\section{Domains}
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et all's baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.

@@

\subsubsection{Navigation domain}

@@

\subsubsection{Traffic domain}
This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}. Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities. This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.

@@

@@

\subsection{Real-World evaluation}

\subsubsection{Navigation domain}

@@

\subsubsection{Traffic Domain}

@@

@@

>>>>

% first the title is needed
\title{Realistically Interesting Domains for Probabilistic Planners}

% a short form should be given in case it is too long for the running head
\titlerunning{Real World Domains}

@@

\section{FF-Replan}
\label{sec:planners}

At the first international probabilistic planning competition IPPC-04, most entries were probabilistic planner using Markov Decision Processes. The winner, FF-Replan \cite{FFReplan}, however was based on deterministic planning techniques. FF-Replan is an action selection algorithm for online planning in probabilistic domains which deals with uncertainty by replanning. FF-Replan generates a deterministic planning problem by determinizing the input domain at the start of the planning. This classical deterministic planning problem allows for the use of the classical FF planner \cite{Hoffmann01theff}. The FF planner then returns an ordered state-action plan for the deterministic problem of the current state mapped in an initially empty hash-table. This plan is executed until an unexpected state, not available in the hash-table is encountered.

If an unexpected state is encountered, the current state, the goal and the domain description are again determinized. The FF planner will generate an ordered plan which is executed until either a goal state, a dead-end state or an unexpected state is reached.

FF-Replan has some obvious shortcomings.Iit first determinizes the input domain and thus removes all probabilistic information from the problem. The success of the planner is therefore fully reliable on the chose determinization heuristic. As FF-replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends. This explains why FF-replan performs poorly in domains containing dead-ends. However, by relying on search FF-replan functions with enormous speed and efficiency and caused the International Conference on Automated Planning and Scheduling (ICAPS) to change their benchmarks to increase their \emph{probabilistically interestingness}. By evaluating and correcting the IPPC-11 domains on their \emph{realistically interestingness} we will draw conclusions whether or not these adjusted realistic domains are actually classical planning problems in disguise - ideal planning problems for FF-replan.

@@

\section{Domains}

% TODO we only look at IPPC-11 domains
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et all's baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.

@@

\subsubsection{Navigation}

@@

\subsubsection{Traffic}
This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}. Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities. This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.

@@

\subsection{Elevators}

In the elevators domain there are a number of elevators delivering passengers
to either the top or bottom floor. Potential passengers arrive at any floor at
a certain rate (depending on which floor). The elevators can only move in the
direction it is indicating, so passengers know whether to board or not. The
goal of the elevators is to transport as many as possible passengers to their
destinations.

\subsection{SysAdmin}

The SysAdmin domain describes a network of connected servers. Each server has
a probability that it shuts down, and if is not running, it has a probability
to reboot. The probability that a server shuts down depends on the number of
running connected servers.

@@

\subsection{Real-World Domain Evaluation}

\subsubsection{Navigation}

@@

\subsubsection{Traffic}

@@

\subsubsection{Elevators}

@@

%----------------------------------------------------------------------------------------
